---
title: "Visualization Final Report"
author: "Me!"
format: 
  html: 
    theme: cosmo
---

## 

## Plotting bank data

As part of a paper that I have out for review right now, I examined the balance sheets of three banks to document the impact of partnering with a fintech risk assessment firm.

I created a database of all U.S. banks loans and leases, which I chopped down to look at these individual banks.

For the data vizualization assignment, I processed the data to chart the percentage of each banks balance sheet devoted to this type of lending category. While this was interesting to see, I think it might be better to map percent change relative to other major lending categories at each bank.

Additionally, if I were to chart this data as is, I would need to remove one acounting category from the data (for small business loans) given that 2/3 banks were active payroll protection program (PPP) lenders and that has a large impact on the data we're seeing for Cross River as the payroll protection program lending tapers off.

Finally, while I was able to get the data processed and the chart working, the functions I found to change the color scheme and the titles on the graph would not work. Not sure why. Any help on that front would be appreciated!

EDIT: After thinking on it for a bit, I think the best way to plot this data may be to calculate the year/year change in major lending categories such as mortgages, small business, real estate, personal loans, etc. and plot this on a graph.

```{r}
library(tidyverse)
library(khroma)
library (ggbeeswarm)
```

```{r}
# firstfed_plot <-
ggplot(banks_database_20230203, aes(x = Year, y = lnconoth)) +
  geom_line(color = "red") 
  #   facet_wrap(
  #   ~name,
  #   labeller = label_both
  # )+
  #   labs(title = "Loans & Leases")

# firstfed_plot <-
# ```
```

```{r}
# bank_baseplot <-
ggplot(banks_database_20230203, aes(x = Year, y = lnconoth, color = name)) +
  geom_line() 
  #   facet_wrap(
  #   ~name,
  #   labeller = label_both
  # )+
    # labs(title = "Loans & Leases")

# bank_baseplot
# ```
```

```{r}
banks_database_20230203 |> 
  filter (Year == c(2017, 2018, 2019, 2020, 2021)) |>
  # filter (name == "FIRST FEDERAL BANK OF KANSAS CITY") |>
   mutate(
    .by = c(Qtr),
    prop = lnconoth/lnlsgr
  ) |>
  ggplot(aes(Year, prop, fill = lnconoth))+
  geom_area()+
  facet_wrap(~name)
  labs(title="Plot of length \n by dose",
        x ="Dose (mg)", y = "Teeth length") +
  scale_fill_brewer(palette = "Dark2") 
 

```
